The Hot Hand Fallacy in Call of Duty Search and Destroy

### 2022-08-30 paper/paper.Rmd
rm gt

cod_round_win_prop_after_k_wins |> filter(win_round, notional_p_value_adj < 0.05)
cod_round_win_prop_after_k_wins |> filter(win_round, ms_p_value_adj < 0.05)

cod_round_win_prop_after_k_wins |> 
  filter(win_streak == 3L) |> 
  mutate(
    across(
      matches('p_value'), 
      ~case_when(
        .x <= 0.01 ~ '<=0.01', 
        TRUE ~ sprintf('%.2f', .x)
      )
    ),
    prop_lab = sprintf('%.1f', 100 * prop),
    notional_lab = sprintf('%.1f (%s)', 100 * notional_prop, notional_p_value_adj),
    ms_lab = sprintf('%.1f (%s)', 100 * ms_prop, ms_p_value_adj)
  ) |>
  arrange(n_rounds, win_series, win_round) |> 
  filter(win_round) |> 
  transmute(
    n_rounds,
    across(win_series, ~ifelse(.x, 'yes', 'no')),
    n,
    total,
    prop_lab,
    notional_lab,
    ms_lab
  ) |> 
  gt::gt() |> 
  gt::cols_label(
    n_rounds = 'r',
    win_series = 'Win series?',
    n = 'r+',
    total = 'N',
    prop_lab = 'O',
    notional_lab = 'a',
    ms_lab = 'b'
  ) |> 
  gt::as_latex() |> 
  cat()
```

@@

cod_round_win_prop_after_k_wins_i_rounds |> filter(notional_p_value < 0.05)
cod_round_win_prop_after_k_wins_i_rounds |> filter(notional_p_value_adj < 0.05)

cod_round_win_prop_after_k_wins_i_rounds |> 
  filter(
    n_rounds >= 7,
    (round + 2) >= n_rounds,
    win_streak == 3L
  ) |> 
  mutate(
    across(
      matches('p_value'), 
      ~case_when(
        .x <= 0.01 ~ '<=0.01', 
        TRUE ~ sprintf('%.2f', .x)
      )
    ),
    prop_lab = sprintf('%.1f', 100 * prop),
    notional_lab = sprintf('%.1f (%s)', 100 * notional_prop, notional_p_value_adj)
  ) |>
  arrange(n_rounds, win_series, win_round) |> 
  filter(win_round) |> 
  transmute(
    n_rounds,
    round,
    across(win_series, ~ifelse(.x, 'yes', 'no')),
    n,
    total,
    prop_lab,
    notional_lab
  ) |> 
  arrange(n_rounds, round, win_series) |> 
  gt::gt() |> 
  gt::cols_label(
    n_rounds = 'r',
    round = 'i',
    win_series = 'Win series?',
    n = 'r+',
    total = 'N',
    prop_lab = 'O',
    notional_lab = 'a'
  ) |> 
  gt::as_latex() |> 
  cat()
```

@@

cod_round_arrangements_naive <- cod_expected_round_arrangements_naive |> perform_run_tests()
cod_round_arrangements_mle <- cod_expected_round_arrangements_mle |> perform_run_tests()

cod_round_arrangements_mle |> 
  filter(!is.na(p_value)) |> 
  filter(is_significant) |> 
  mutate(
    total_actual = sum(n_actual),
    total_expected_adj = sum(n_expected_adj)
  ) |>
  mutate(
    prop_p_value = vectorized_prop_test(
      n_actual, 
      total_actual, 
      round(n_expected_adj), 
      round(total_expected_adj)
    )$p.value,
    across(prop_p_value, list(adj = ~p.adjust(.x, method = 'BY'))),
    across(
      matches('p_value'), 
      ~case_when(
        .x <= 0.01 ~ '<=0.01', 
        TRUE ~ sprintf('%.2f', .x)
      )
    ),
    across(ws, ~str_replace_all(.x, '-', ' ') |> str_replace_all(c('1' = '+', '0' = '-'))),
    actual_lab = sprintf('%.2f', 100 * prop_actual),
    expected_lab = sprintf('%.2f (%s)', 100 * prop_expected, prop_p_value)
  ) |> 
  select(
    n_rounds, 
    ws,
    n_actual,
    actual_lab,
    n_expected,
    expected_lab
  ) |> 
  arrange(n_rounds, ws) |> 
  filter(n_rounds <= 10) |> 
  gt::gt() |> 
  gt::cols_label(
    n_rounds = 'r',
    ws = 'zeta',
    n_actual = 'n1',
    actual_lab = 'p1',
    n_expected = 'n2',
    expected_lab = 'p2'
  ) |> 
  gt::as_latex() |> 
  cat()
```

>>>>

cod_round_win_prop_after_k_wins |> filter(win_round, notional_p_value_adj < 0.05)
cod_round_win_prop_after_k_wins |> filter(win_round, ms_p_value_adj < 0.05)
```

@@

cod_round_win_prop_after_k_wins_i_rounds |> filter(notional_p_value < 0.05)
cod_round_win_prop_after_k_wins_i_rounds |> filter(notional_p_value_adj < 0.05)
```

@@

cod_round_arrangements_naive <- cod_expected_round_arrangements_naive |> perform_run_tests()
cod_round_arrangements_mle <- cod_expected_round_arrangements_mle |> perform_run_tests()
```
